Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-09-27 docs/Manuscript.tex
Updated scripts and manuscript

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement effects in PIPA},
            pdfauthor={Juan Carlos Villaseñor-Derbez},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\usepackage[normalem]{ulem}
% avoid problems with \sout in headers with hyperref:
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{Displacement effects in PIPA}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Juan Carlos Villaseñor-Derbez}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \date{}
  \predate{}\postdate{}

@@

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}
\maketitle

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\emph{Last update: 2018-09-14}

\section{To do}\label{to-do}

@@

  \begin{itemize}
  \tightlist
  \item
    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
  \item
    {[} {]} B: Taiwan, Never in PNA, Similar region
  \end{itemize}
\item
  {[}x{]} Change in fishing hours before vs after
\item
  {[} {]} \sout{Change in total hours before vs after}
\item
  {[} {]} Change in distance before vs after
\item
  {[} {]} Where do PIPA vessels go?
\item
  {[} {]} Make sure I have full tracks of all mmsis
\end{itemize}

@@

@@

@@

The Global Fishing Watch (GFW) data contain 233 vessels that have fished
within PIPA waters. From these, 217 did so at least once before 2015,
but only 183 continued to fish after 2015. The 34 missing vessels might
tell us something about the impact of PIPA. However, they might have
gone to other areas (i.e.~outside of PNA countries). I must dig deeper
into this.

Accounting for the fact that vessels that fished within PIPA before
implementation might stop fishing afterwards, or that vessels entered
the fishery after PIPA closure, I define my treatment and control groups
as follows. The treatment group contains all vessels that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. The Control group has vessels that never fished
within PIPA waters, belong to other PNA countries, and have fished in
surroinding areas before and after PIPA closure. Tables
\ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the
number of vessels, number of vessels following a BACI design, and
fishing hours, respectively. Tables show data grouped by gear
(longlines, purse seines), group (treated, control), and period (before,
after). The relative change (After / Before) is also shown. Table
\ref{tab:baci_n} shows information for all fishing vessels in the
dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show
information for vessels that meet the BACI design (i.e.~excludes vessels
that only appear at one point in time).

>>>>

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{nature}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\usepackage[normalem]{ulem}
% avoid problems with \sout in headers with hyperref:
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-09-27}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1} Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, CA
\textsuperscript{2} Department of Economics, University of Hawaii at
Manoa, Honolulu, HI}

@@

\begin{document}
\maketitle
\begin{abstract}
Large-scale Marine Protected Areas (LSMPAs) have seen a significant
increase over the last years. Fishing effort is effectively eliminated
within these protected areas upon implementation. The benefits of
reducing effort have been largely studied, and include increases in
abundance, biomass, and diversity within the bounded regions. These
no-take zones may produce spillover effects, which provide fish for
outside areas. However, the economic and ecological implications of
displacing fishing effort are not yet fully understood. Novel data
products that track fishing effort at the vessel-level allow us to
identify changes in fleet- and vessel-level behavior upon the
implementation of protected areas, as well as how these redistribute.
This papers evaluates the implications of implementing LSMPA, by
evaluating changes in fishing hours, showing that vessels in the
effected region reduce fishing effort after the implementation of PIPA.
Our results are robust to a set of specifications. We also track the
relative spatial allocation of fishing events thorugh time, and identify
that areas closer to PIPA show an increase in relative fishing hourse
due to the displacement of PIPA-fishing vessels. Our results not only
provide an impact evaluation of the effect of LSMPAs on fishing
activity, but provide insights into vessel redistribution dynamics,
which may have ecological and economic implications.
\end{abstract}

{
\setcounter{tocdepth}{4}
\tableofcontents
}
\section{To do}\label{to-do}

@@

  \begin{itemize}
  \tightlist
  \item
    {[}x{]} A: PNA, similar vessel, never fished inside PIPA
  \item
    {[} {]} \sout{B: Taiwan, Never in PNA, Similar region}
  \end{itemize}
\item
  {[}x{]} Change in fishing hours before vs after
\item
  {[} {]} \sout{Change in total hours before vs after}
\item
  {[} {]} Change in distance before vs after
\item
  {[}x{]} Where do PIPA vessels go?
\item
  {[}x{]} Make sure I have full tracks of all mmsis
\end{itemize}

@@

\section{Introduction}\label{introduction}

This work identifies the behavioral changes of fishing vessels due to
the implementation of PIPA. Not only can we identify temporal changes in
fishing patterns (\emph{i.e.} time and distance), but also spatial
patterns. Our vessel-level tracks allow us to see where PIPA-fishing
vessels go after the closure, providing empirical insights about the
redistribution of fishing effort after the implementaion of a MPA.

@@

This section is divided into two main parts. First, we provide a general
description of AIS data and the process of identification of
vessel-level events done by Global Fishing Watch \footnote{\href{globalfishingwatch.org}{Global
  Fishing Watch}}. Alongside, we describe the subset of data that we use
for these analyses. When relevant, we also point out possible
shortcommings in the data, or factors that must be considered in the
later analyses. Then we move on to explain our identification strategy,
and the main analyses that we undertake.

@@

\subsubsection{AIS data}\label{ais-data}

Automatic Identification Systems are on-board devices intended to
provide at-sea saftey and prevent ship collisions by broadcasting vessel
locations to surrounding vessels. These broadcasted positions can be
recorded by satellites and land-based antenas. GFW uses a neural network
to infer vessel characteristics and whether each broadcasted position
represents a fishing event, thus allowing us to estimate near real-time
fishing events globally \citep{kroodsma_2018}. The recent addition of
satellites that can receive AIS signals causes an apparent increase in
the number of broadcasted AIS messages (\emph{i.e.} points) and
therefore fishing hours. It is therefore important to be cautious when
comparing temporal trends. The variability in AIS data and dynamic ocean
conditions require that temporal trends be taken into account. We do
that by incorporating a series of controls, which are defined in the
following section.

\subsubsection{PIPA data}\label{pipa-data}

The GFW data contain 233 purse seiners and longliners that have fished
within PIPA waters. From these, only 217 did so at least once before
2015, but only 183 continued to fish after 2015\footnote{The 34 missing
  vessels might have exited the fishery, been decomissioned or sold
  (therefore chaning their AIS and mmsi), or turned off their AIS
  transmiters. On either case, we are not able to observe these.}.
Vessels that fished within PIPA before implementation might stop fishing
afterwards, therefore not being observable in the post-treatment period.
New vessels might have also entered the fishery after PIPA closure, and
were likely not exposed to the policy intervention in the pre-treatment
period. Therefore, we define our treatment and control groups as
follows. The treatment group contains all vessels that fished within
PIPA at least once before the closure, and that continued to fish
elsewhere afterwards. The control group has vessels that never fished
within PIPA waters, belong to other PNA countries, and have fished in
surrounding areas (\emph{i.e.} PNA-countries' EEZ) before and after PIPA
closure. Figure \ref{fig:baci_strict} provides a visual representation
of the vessel-level that make up each of group through time.

Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show
the number of vessels, number of vessels following a BACI design, and
fishing hours, respectively. Tables show data grouped by gear
(longlines, purse seines), group (treated, control), and period (before,
after). The relative change (After / Before) is also shown. Table
\ref{tab:baci_n} shows information for all fishing vessels in the
dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show
information for vessels that meet the BACI design (i.e.~excludes vessels
that only appear at one point in time).

\begin{figure}
\centering
\includegraphics{../img/BACI_strict_gear.png}
\caption{\label{fig:baci_strict}Stream of fishing events by vessels
(stacked on the y-axis due to space) through time (x-axis). Each dot
represent a vessel-month, with colors indicating the pre and post
periods, and pannels separating between gear and treated or control
groups.}
\end{figure}

### 2018-09-27 rmd/Manuscript.Rmd
Updated scripts and manuscript

---
title: "Displacement effects in PIPA"
author: "Juan Carlos Villaseñor-Derbez"
# abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years. Literature shows that fishing effort is effectively eliminated in this protected areas upon implementation. The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions. In terms of the fishing implication, no-take zones may produce spillover that provide fish for outside areas. The implications of displacement of fishing effort are not yet fully understood. Evidence suggests that fishing effort re-distributes along the borders of the MPA, following an ideal free distribution. Novel data products allow us to track fishing effort at the vessel-level, allowing us to identify changes in behavior at both the fleet and vessel level. This papers evaluates the implications of implementing a LMPA, the Phoenix Islands Protected Area (PIPA). We evaluate changes in fishing effort, and track vessels to see where they go after the implementation of PIPA. Our results show that vessels in the effected region increase fishing effort after the implementation of PIPA. THey are redistributed to X. These findings have major implications for MPA implementation, especially as countries rush to meet the goals of 10% ocean protection as mandated by the SDG."
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 4
    citation_package: natbib
    keep_tex: yes
    number_sections: no
header-includes:
  - \usepackage{float}
  - \floatplacement{figure,table}{H}
bibliography: references.bib
biblio-style: nature
---

*Last update: `r Sys.Date()`*

@@

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

# To do

- [x] Divide pipa vessels by type of boat (longline vs. purse seine)
- [x] Identify two counterfactuals:
    -  [x] A: PNA, similar vessel, never fished inside PIPA
    - [ ] B: Taiwan, Never in PNA, Similar region
- [x] Change in fishing hours before vs after
- [ ] ~~Change in total hours before vs after~~
- [ ] Change in distance before vs after
- [ ] Where do PIPA vessels go?
- [ ] Make sure I have full tracks of all mmsis

@@

@@

@@

@@

n_post <- effort_by_vessel %>% 
  filter(treated, post, baci_strict) %$%
  unique(mmsi) %>% 
  length()

```

The Global Fishing Watch (GFW) data contain `r pipa_vessels` vessels that have fished within PIPA waters. From these, `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015. The `r n_prev - n_post` missing vessels might tell us something about the impact of PIPA. However, they might have gone to other areas (i.e. outside of PNA countries). I must dig deeper into this.

Accounting for the fact that vessels that fished within PIPA before implementation might stop fishing afterwards, or that vessels entered the fishery after PIPA closure, I define my treatment and control groups as follows. The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards. The Control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surroinding areas before and after PIPA closure. Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively. Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after). The relative change (After / Before) is also shown. Table \ref{tab:baci_n} shows information for all fishing vessels in the dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show information for vessels that meet the BACI design (i.e. excludes vessels that only appear at one point in time).

@@

The current approach is to estimate what percentage of fishing effort from the PNA was displaced by PIPA and use this to infer something about Palau. While this provides a measure of the displacement, it does not fully address the possibility of costs increasing. I believ we can use individual tracks (as opposed to just the gridded effort) and obtain show how their behavior changed (*i.e.* are they fishing further away, are they fishing more, where are they now?).

### Model specifications

@@

Our model specification uses a DiD approach. In this case, we interact the before-after dummy with a treatment dummy. The treatment and control groups follow our definition in the data description. The model takes the form of:

$$
H_{ijkl} = \alpha + \beta Post_i \times Treat + \mu_j + \phi_k + \gamma_l+ \epsilon_{ijk}
$$

Where $\mu_j$, $\phi_k$, and $\gamma_l$ represent month-, year-, and flag-level fixed effects. I use total hours at the vessel-month level.

>>>>

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
subtitle: "Updated on `r Sys.Date()`"
author: |
  Juan Carlos Villaseñor-Derbez^1^
  John Lynham^2^
abstract: "Large-scale Marine Protected Areas (LSMPAs) have seen a significant increase over the last years. Fishing effort is effectively eliminated within these protected areas upon implementation. The benefits of reducing effort have been largely studied, and include increases in abundance, biomass, and diversity within the bounded regions. These no-take zones may produce spillover effects, which provide fish for outside areas. However, the economic and ecological implications of displacing fishing effort are not yet fully understood. Novel data products that track fishing effort at the vessel-level allow us to identify changes in fleet- and vessel-level behavior upon the implementation of protected areas, as well as how these redistribute. This papers evaluates the implications of implementing LSMPA, by evaluating changes in fishing hours, showing that vessels in the effected region reduce fishing effort after the implementation of PIPA. Our results are robust to a set of specifications. We also track the relative spatial allocation of fishing events thorugh time, and identify that areas closer to PIPA show an increase in relative fishing hourse due to the displacement of PIPA-fishing vessels. Our results not only provide an impact evaluation of the effect of LSMPAs on fishing activity, but provide insights into vessel redistribution dynamics, which may have ecological and economic implications."
date: |
  ^1^Bren School of Environmental Science and Management, University of California Santa Barbara, Santa Barbara, CA
  ^2^Department of Economics, University of Hawaii at Manoa, Honolulu, HI
output:
  bookdown::pdf_document2:
    toc: yes
    toc_depth: 4
    citation_package: natbib
    keep_tex: yes
    number_sections: no
header-includes:
  - \usepackage{float}
  - \floatplacement{figure,table}{H}
bibliography: references.bib
biblio-style: nature
---

@@

knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

options(knitr.table.format = "latex")
```

@@

# Introduction

This work identifies the behavioral changes of fishing vessels due to the implementation of PIPA. Not only can we identify temporal changes in fishing patterns (*i.e.* time and distance), but also spatial patterns. Our vessel-level tracks allow us to see where PIPA-fishing vessels go after the closure, providing empirical insights about the redistribution of fishing effort after the implementaion of a MPA.

@@

This section is divided into two main parts. First, we provide a general description of AIS data and the process of identification of vessel-level events done by Global Fishing Watch [^1]. Alongside, we describe the subset of data that we use for these analyses. When relevant, we also point out possible shortcommings in the data, or factors that must be considered in the later analyses. Then we move on to explain our identification strategy, and the main analyses that we undertake.

[^1]: [Global Fishing Watch](globalfishingwatch.org)

@@

### AIS data

Automatic Identification Systems are on-board devices intended to provide at-sea saftey and prevent ship collisions by broadcasting vessel locations to surrounding vessels. These broadcasted positions can be recorded by satellites and land-based antenas. GFW uses a neural network to infer vessel characteristics and whether each broadcasted position represents a fishing event, thus allowing us to estimate near real-time fishing events globally \citep{kroodsma_2018}. The recent addition of satellites that can receive AIS signals causes an apparent increase in the number of broadcasted AIS messages (*i.e.* points) and therefore fishing hours. It is therefore important to be cautious when comparing temporal trends. The variability in AIS data and dynamic ocean conditions require that temporal trends be taken into account. We do that by incorporating a series of controls, which are defined in the following section.

### PIPA data

@@

n_post <- effort_by_vessel %>% 
  filter(treated, post, baci_strict) %$%
  unique(mmsi) %>% 
  length()
```

The GFW data contain `r pipa_vessels` purse seiners and longliners that have fished within PIPA waters. From these, only `r n_prev` did so at least once before 2015, but only `r n_post` continued to fish after 2015[^2]. Vessels that fished within PIPA before implementation might stop fishing afterwards, therefore not being observable in the post-treatment period. New vessels might have also entered the fishery after PIPA closure, and were likely not exposed to the policy intervention in the pre-treatment period. Therefore, we define our treatment and control groups as follows. 
The treatment group contains all vessels that fished within PIPA at least once before the closure, and that continued to fish elsewhere afterwards. The control group has vessels that never fished within PIPA waters, belong to other PNA countries, and have fished in surrounding areas (*i.e.* PNA-countries' EEZ) before and after PIPA closure. Figure \ref{fig:baci_strict} provides a visual representation of the vessel-level that make up each of group through time.

Tables \ref{tab:baci_n}, \ref{tab:baci_n_s}, and \ref{tab:baci_h} show the number of vessels, number of vessels following a BACI design, and fishing hours, respectively. Tables show data grouped by gear (longlines, purse seines), group (treated, control), and period (before, after). The relative change (After / Before) is also shown. Table \ref{tab:baci_n} shows information for all fishing vessels in the dataset, while Tables \ref{tab:baci_n_s} and \ref{tab:baci_h} show information for vessels that meet the BACI design (i.e. excludes vessels that only appear at one point in time).

![\label{fig:baci_strict}Stream of fishing events by vessels (stacked on the y-axis due to space) through time (x-axis). Each dot represent a vessel-month, with colors indicating the pre and post periods, and pannels separating between gear and treated or control groups.](../img/BACI_strict_gear.png)

[^2]: The `r n_prev - n_post` missing vessels might have exited the fishery, been decomissioned or sold (therefore chaning their AIS and mmsi), or turned off their AIS transmiters. On either case, we are not able to observe these.

@@

### Change in behavior

The first analysis focuses on identifying the response of fishing vessels to PIPA closure. Our variables of interests are fishing effort, indicated by total fishing hours per month, and distance traveled (Km) on every fishing trip. We compare fishing hours[^3] before and after the implementation of PIPA using a Difference-in-Differences approach, where we track the variable of interest for vessels that used to fish inside PIPA and vessels that never fished inside PIPA, before and after PIPA implementation. Our specification is the following:

$$
y_{i,t} = \alpha + \beta Post_t \times Treat_i + \mu_t + \phi_t + \gamma_i + \epsilon_{it}
$$

Where $y_{ijkl}$ is the variable of interest for vessel $i$ in time period $t$. $\alpha$ is the standard intercept, and $\beta$ is our parameter of interest: de DiD estimate capturing the treatment effect. A dummy variable $Post_i$ takes the value of 0 for all dates prior to PIPA implementation and a value of 1 por all dates including and following PIPA implementation date. $Treat_i$ is a dummy variable indicating whether a vessel belongs to the control ($Treat_i = 0$) or treatment ($Treat_i = 1$) group. Finally, $\mu_t$, $\phi_t$, and $\gamma_i$ represent month-, year-, and flag-level dummies that account for seasonality or country-level management interventions.

[^3]: And soon, distance

@@

### Vessel displacement and redistribution
